Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-10-09 manuscript2.RMD
updates

The main findings of the present study were that heavy resistance training with glucose did not affect markers of ribosome biogenesis, measured as total RNA, rRNA, and rDNA transcription initiation-associated proteins, compared to RT with placebo. Similarly, RT with glucose in general did not affect markers of skeletal muscle functionality such as strength and recovery, or total training session volume. Towards the end of the intervention, RT with glucose led to less reduction in strength compared to placebo. Levels of plasma glucose and c-peptide were significantly higher before, during and after the RT sessions with glucose. Importantly, there were no differences in daily macronutrient intake on pairwise consecutive days. These findings suggest that the effects of high vs. low glucose/glucose starvation conditions on rDNA transcription initiation observed in previous *in vitro* studies [@mariappan_ribosomal_2011; @tanaka_mild_2015] are not translatable to acute effects in human skeletal muscle *in vivo*. Notably, the present study was specifically designed to investigate differences in pre to post changes within participants and is as such also quite limited to this perspective. Hence, the observed effects of time serve as supplementary to the efficiency of the design, without a negative control group to compare with.

@@

In the present study, despite not measuring the activity in central pathways mediating anabolic signalling (mTORC1, ERK1/2), analyses of the downstream target UBF and the ribosomal protein S6 (rpS6), as well as the general transcription factor c-Myc, further supported observations from the RNA data. UBF has previously been described as a master regulator of rDNA transcription *in vitro* [@figueiredo_regulation_2019; @kusnadi_regulation_2015; @russell_rna-polymerase-i-directed_2005], while rpS6 is proposed as a valid and reliable means to measure ribosome biogenesis [@chaillou_hypoxia_2012; @nakada_correlation_2016]. Lastly, c-Myc has previously been described as a potent regulator of ribosome biogenesis, independent of mTORC1, and a direct regulator of UBF [@mori_c-myc_2021; @poortinga_c-myc_2011; @west_acute_2016]. Hence, it seems quite reasonable to observe similar changes in these three proteins. The linear relationship found exclusively between UBF content and total RNA accumulation, and neither c-Myc nor rpS6, supports the importance and specificity of UBF content in human skeletal muscle ribosome biogenesis. While this is not a novel finding, it has only recently been observed in human skeletal muscle following RT [@hammarstrom_ribosome_2022]. As such, UBF also seems to respond to mechanical loading in human muscle cells in line with responses seen in cell cultures and synergist ablation models [@mariappan_ribosomal_2011; @von_walden_mechanical_2012], in addition to the previously reported response to hormonal, nutritional, and cellular energy signals [@figueiredo_regulation_2019; @kusnadi_regulation_2015; @russell_rna-polymerase-i-directed_2005].

>>>>

The main findings of the present study were that heavy resistance training with glucose did not affect markers of ribosome biogenesis, measured as total RNA, rRNA, and rDNA transcription initiation-associated proteins, compared to RT with placebo. Similarly, RT with glucose in general did not affect markers of skeletal muscle functionality such as strength and recovery, or total training session volume. Towards the end of the intervention, RT with glucose led to less reduction in strength compared to placebo, which may point to an accumulated effect of the glucose condition. As by design the levels of plasma glucose and c-peptide were significantly higher before, during and after the RT sessions with the glucose condition compared to placebo, and there were no differences in the daily macro nutrient intake between conditions on consecutive days, thus enabling an effective design to study the biological and functional effects of the glucose condition. These findings suggest that the effects of high vs. low glucose/glucose starvation conditions on rDNA transcription initiation observed in previous *in vitro* studies [@mariappan_ribosomal_2011; @tanaka_mild_2015] are not translatable to acute effects in human skeletal muscle *in vivo*, with a design as the present study. Notably, the present study was specifically designed to investigate differences in pre to post changes within participants and is as such also quite limited to this perspective. Hence, the observed effects of time serve as supplementary to the efficiency of the design, without a negative control group to compare with.

@@

In the present study, despite not measuring the activity in central pathways mediating anabolic signalling (mTORC1, ERK1/2), analyses of the downstream target UBF and the ribosomal protein S6 (rpS6), as well as the general transcription factor c-Myc, further supported observations from the RNA data. UBF has previously been described as a master regulator of rDNA transcription *in vitro* [@figueiredo_regulation_2019; @kusnadi_regulation_2015; @russell_rna-polymerase-i-directed_2005], while rpS6 is proposed as a valid and reliable means to measure ribosome biogenesis [@chaillou_hypoxia_2012; @nakada_correlation_2016]. Lastly, c-Myc has previously been described as a potent regulator of ribosome biogenesis, independent of mTORC1, and a direct regulator of UBF [@mori_c-myc_2021; @poortinga_c-myc_2011; @west_acute_2016]. Hence, it seems quite reasonable to observe similar changes in these three proteins. The linear relationship found exclusively between UBF content and total RNA levels, and neither c-Myc nor rpS6, supports the importance and specificity of UBF content in human skeletal muscle ribosome biogenesis. While this is not a novel finding, it has only recently been observed in human skeletal muscle following RT [@hammarstrom_ribosome_2022]. As such, UBF also seems to respond to mechanical loading in human muscle cells in line with responses seen in cell cultures and synergist ablation models [@mariappan_ribosomal_2011; @von_walden_mechanical_2012], in addition to the previously reported response to hormonal, nutritional, and cellular energy signals [@figueiredo_regulation_2019; @kusnadi_regulation_2015; @russell_rna-polymerase-i-directed_2005].
